---
title: "mouseCMS"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mouseCMS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)
```
```{r setup}
library(mouseCMS)
```
An R package for subtyping mouse models into CMSs and an example dataset provided to run the `mouseCMSclassifier`.

To install the `mouseCMS`, use `devtools`:

```{r eval=FALSE}
    library(devtools)
    install_github("atorang/mouseCMS")
```

To run the demo below, you need to first load package and a dataset:

```{r eval=FALSE}
    library(mouseCMS)
    load("exprs.test")
```

Now you can classify the data using an elastic-net model: The function has only two arguments, `data` which is a numeric matrix or data.frame with expression levels. Rows are genes and columns are samples. Ensemble Ids are used. And `log2Transformation` which is a logical determining if data needs log2-transformation or if the data is already log2-transformed. Default is `log2Transformation = FALSE`.

```{r eval=FALSE}
    res <- mouseCMSclassifier(data=exprs.test, log2Transformation=FALSE)
```
